Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-03 qhtv2.tex
Nettoyage

\subsection{Bounds on the Duplicate Detection over a Sliding Window Problem}

\begin{theorem}
	Let $W$ be a sliding window size, and let us consider a duplicate detection problem over $W$. If the available amount of memory $M$ is such that $M \simeq 2W\log_2W$, then the problem can be solved with almost no error.
\end{theorem}

\begin{proof}
Let us consider a duplicate detection problem of a stream $E$ over a sliding window $W$. We first devise a hash function, whose fingerprints are $2 \log_2 W$ bits long.

The birthday paradox, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $H$ over $a$ bits, one must, on average, collect $2^{a/2}$ hashes of different messages before obtaining a collision. Hence, in our case, we can store $2^{2 \log_2 W / 2} = W$ fingerprints of different elements before having a collision, i.e., two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ which have the same hash, i.e. $H(e_i) = H(e_j)$.

Hence, one can construct a filter $\mathcal F$ which consists in a queue of $W$ hashes: for each new element $e$, \textsf{Detect}(e) returns \DUPLICATE if $H(e)$ is present in the queue, \UNSEEN otherwise. \textsf{Insert}(e) just adds $H(e)$ to the queue before popping the list. There is no false negative, and a false positive only happens if two elements have the same hash, which does not happen often, hence a low FPR and a null FNR.

The queue stores $W$ hashes, and as such requires $W \cdot 2\log_2 W$ bits of memory.
\end{proof}

>>>>

\subsection{Bounds on the Sliding Window DDP}

\begin{theorem}
	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.
\end{theorem}

\begin{proof}
	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision. Therefore $2^{2 \log_2 w / 2} = w$ values $h(e_i)$ can be computed before having a collision, i.e., two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ which have the same hash, i.e. $h(e_i) = h(e_j)$.

Let $\mathcal F$ be the following filter: the filter's state consists in a queue of $w$ hashes, and for each new element $e$, $\mathsf{Detect}(e)$ returns \DUPLICATE if $h(e)$ is present in the queue, \UNSEEN otherwise. $\mathsf{Insert}(e)$ appends $h(e)$ to the queue before popping the list.

There is no false negative, and a false positive only happens if two elements have the same hash, which does not happen often, hence a low FPR and a zero FNR.
The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
\end{proof}
